%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% % !TEX TS-program = xelatex
%%% % !TEX encoding = UTF-8 Unicode
%%% % !Mode:: "TeX:UTF-8"
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume}

%%% \usepackage{zh_CN-Adobefonts_external}

\newif\ifus
\newif\ifcn

\newcommand{\us}[1]{\ifus#1\fi}
\newcommand{\cn}[1]{\ifcn#1\fi}

% \cntrue
\ustrue

\newif\ifen
\newif\ifzh
\newif\ifboth

\newcommand{\en}[1]{\ifen#1\fi}
\newcommand{\zh}[1]{\ifzh#1\fi}
\newcommand{\both}[1]{\ifboth#1\fi}

\entrue
% \zhtrue
\ifzh\ifen\bothtrue\fi\fi

\begin{document}
    \en{\us{\name{Tony Chen}}
    \cn{\name{Sibei Chen}}}
    \zh{\name{陈思贝}}

    \basicInfo{
        \email{tonychensibei@gmail.com} $\cdot$ 
        \cn{\phone{(+86) 138-1757-6706}}
        \us{\phone{(+1) 240-825-8413}} $\cdot$ 
        \linkedin{Tony Chen}{https://www.linkedin.com/in/tony-chen-922b48171} $\cdot$ 
        \github{TonyCSB}{https://github.com/TonyCSB/}
    }

    % \vspace{.5cm}
    % \en{\textbf{Available after middle Oct. 2020, preferably in the Software Engineering Department.}}
    % \both{\newline}
    % \zh{2020年10月中旬后可以参加实习，希望能进软件工程类的部门。}

    \section{\faAnchor\ \en{Career Objective}}
    \en{Employment as a Software Developer, using my programming and communication skills to code in a team environment.}

    \section{\faGraduationCap\ \en{Education}\both{ }\zh{教育经历}}
    \en{\datedsubsection{University of Maryland}{Aug. 2018 -- Dec. 2021}}
    \zh{\datedsubsection{美国马里兰大学}{2018年8月 -- 2021年12月}}
    \en{\role{Bachelor of Science}{}}
    \zh{\role{科学学士学位}{}}
    \en{Major in Computer Science. Minor in General Business.\\
    Expected to Graduate: December 2021\\
    Cumulative GPA: 3.90}\both{\newline}
    \zh{计算机科学专业，辅修商科。\\
    预计毕业时间：2021年12月\\
    总计GPA：3.90}

    \section{\faUsers\ \en{Experience}\both{ }\zh{工作与实习经历}}
    \en{\datedsubsection{SAIC Motor Passenger Vehicle Company}{Jul. 2020 -- Oct. 2020}}
    \zh{\datedsubsection{上汽集团}{2020年7月 -- 2020年10月}}
    \en{\role{Software Intern}{}}
    \zh{\role{软件实习生}}
    \en{Worked on the embedded system andcomputer vision system for consumer vehicles. Experienced in coding with a team.}\both{\newline}
    \zh{车载嵌入式系统研发，熟悉AUTOSAR系统。}

    \en{\datedsubsection{Morgan Stanley Huaxin Securities Co., Ltd.}{Apr. 2020 -- Jul. 2020}}
    \zh{\datedsubsection{摩根士丹利}{2020年4月 -- 2020年7月}}
    \en{\role{Intern}{Board of Directors Office}}
    \zh{\role{实习生}{董事会办公室}}
    \en{Participated in the 51\% equity transfer of Morgan Stanley Huaxin Securities Co., Ltd. in Shanghai. 
    Took leads in the modification of its policies and rules, such as \textit{Corporate Governance Policy}, 
    in compliance with those of Morgan Stanley's. Have an extensive knowledge on securities regulation set 
    forth by China Securities Regulatory Commission. }\both{\newline}
    \zh{参与了摩根士丹利对摩根士丹利华鑫证券有限责任公司的51\%股权的收购。参与起草修改了摩根华鑫的《公司治理制度》等一系列的规章制度。
    对公司的治理以及中国证券监督管理委员会的对行业监管监督工作有着较为深刻的了解}

    \en{\datedsubsection{University of Maryland}{Oct. 2019 -- Jul. 2020}}
    \zh{\datedsubsection{美国马里兰大学}{2019年10月 -- 2020年7月}}
    \en{\role{Student Driver}{Shuttle UM}}
    \zh{\role{学生司机}{}}
    \en{Student shuttle driver at University shuttle team. Acquired Commercial Driver's License through rigorous training in my spare time.}\both{\newline}
    \zh{我是马里兰大学校车的一名司机，经过严格的训练，我在课余时间考到了商用B级驾照。这份工作体现了我的守时的个性与为公众服务的理想。}

    \en{\datedsubsection{University of Maryland}{Sep. 2018 -- Dec. 2019}}
    \zh{\datedsubsection{美国马里兰大学}{2018年9月 -- 2019年12月}}
    \en{\role{Research Assistant}{Department of Human Development and Quantitative Methodology}}
    \zh{\role{研究助理}{}}
    \en{Data entry, literature review and basic data compiling for cognitive diagnosis modeling.
    Provides visual interpretation and analysis presentations.}\both{\newline}
    \zh{为认知分析建模进行数据输入，文学评估与数据分析。}

    \en{\datedsubsection{Rural Teacher Training}{Summer 2015 -- Summer 2018}}
    \en{\role{Volunteer}{Event Organizer}}
    \en{Selects teachers serving in under-developed region in China and provides them with training from professionals
    in education field during summer break. Organized several entertainment events with over 500 audiences. Had extensive experience 
    in communicating with vendors and sponsors.}

    \section{\faCogs\ \en{Skills}\both{ }\zh{技能}}
    \begin{myitemize}
        \item \en{Languages}\both{ }\zh{语言}: \en{English - Proficient, Chinese - Native}
        \item \en{Programming Languages}\both{ }\zh{编程语言}: Python, Java, \LaTeX, Swift, C, Ruby, Ocaml, SQL
        \item \en{Platform}\both{ }\zh{平台}: Windows 10, Linux
        \item \en{Others}\both{ }\zh{其他}: Bash, Javascript, HTML \& CSS
        \item \en{Class B Commercial Drivers' License}
    \end{myitemize}

    \section{\faCertificate\ \en{Honors \& Certificates}\both{ }\zh{荣誉与证书}}
    \begin{myitemize}
        \item Dean's List and Academic Honor in all semesters
        \item Office of Multi-Ethnic Student Education Academic Excellence Awards
        \item Google Cloud Platform Essential Certificate
    \end{myitemize}
\end{document}

